SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/paper.tex
last tweaks to Test Suite for now

The SciPy test suite is orchestrated by a continuous integration matrix that
includes posix and Windows (32/64-bit) platforms managed by Travis CI and
AppVeyor, respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and
include code linting with \texttt{pyflakes} and \texttt{pycodestyle}. There are more than $13,000$
unit tests in the test suite, which uses the \texttt{pytest} framework, and coverage of SciPy's approximately $204000$ lines of code
has held steady at 76.5 \% for the last six months (Figure~\ref{fig:coverage}). 
Documentation for the code is automatically built and hosted by
the CircleCI service to facilitate evaluation of documentation changes/integrity.  
Our full test suite also passes with PyPy3, a just-in-time compiled
version of the Python language.

>>>>

The SciPy test suite is orchestrated by a continuous integration matrix that
includes posix and Windows (32/64-bit) platforms managed by Travis CI and
AppVeyor, respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and
include code linting with \texttt{pyflakes} and \texttt{pycodestyle}. There are more than $13,000$
unit tests in the test suite, which uses the \texttt{pytest} framework, and coverage of SciPy's approximately $204,000$ lines of code
has held steady at 76.5\% for the last six months (Figure~\ref{fig:coverage}). 
Documentation for the code is automatically built and hosted by
the CircleCI service to facilitate evaluation of documentation changes/integrity.  
Our full test suite also passes with PyPy3, a just-in-time compiled
version of the Python language.
